Classless Java

### 2015-11-20 paper/sections/CaseStudy.tex
revised method overriding mechanism in Java

\section{Case studies}
Haoyuan and Yanlin

@@

\lstinputlisting[linerange=25-35]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_INIT

@@

\subsubsection{Adding a New Variant}
It is easy to add new data variants to the code in the initial system in a
modular way. For example, the following code how to add the subtraction variant.

\lstinputlisting[linerange=39-44]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_SUB

@@

\lstinputlisting[linerange=48-57]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_PRINT

>>>>

\section{Case Studies}
Haoyuan and Yanlin

@@

\lstinputlisting[linerange=34-44]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_INIT

@@

\subsubsection{Adding a New Variant}
It is easy to add new data variants to the code in the initial system in a
modular way. For example, the following code shows how to add the subtraction variant.

\lstinputlisting[linerange=48-53]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_SUB

@@

\lstinputlisting[linerange=57-66]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_PRINT
